% !Mode:: "TeX:UTF-8"
% !TEX program  = xelatex
\section{Chapter~7 Summary}
\footnotetext{This article uses the EB Garamond family of fonts, which is designed by Georg Duffner and Octavio Pardo.}\footnotetext{The function of a paragraph indent is to mark a pause, setting the paragraph apart from what precedes it. If a paragraph is preceded by a title or subhead, the indent is superfluous and can therefore be omitted.}
This chapter mainly introduced the writing of other types, including statement, curriculum vit\ae, cover letter, recommendation letter, referee report, and paper review. Although each type has its characteristics, they have commonalities in terms of writing, for example, clear theme, compact structure, fluent statements, appropriate description, and correct grammar. The writing of professional mathematics articles mainly requires the mathematical language, so as long as you master the basic rules of writing, it is generally not abnormal. In addition, language ability cannot be improved by reading only a few guide books. Instead, you should read a lot of works written by others, and put what you learned into practice.



\section{Application}
The application letter is a common type, and this chapter mainly discusses some writing methods for the admission application and the job application letter.

To apply for admission to European or American universities, you not only need to fill out the application form, but also request to write a statement, which requires to explain the motivation for applying, personal characteristics, and the plan for the future, etc. It should be noted that unmodified templates cannot be used when writing the statement, you should use your personal experience to explain thoughts, instead. Moreover, preparing a personal resum\'e with elegant format and clear content is useful, as well. However, under the premise of listing innovative projects, the records must be real.

The cover letter in the job application materials of the position application should not be too long, because the professional background has been detailed in the resum\'e, there is no need to repeatedly emphasize the advantages in the letter. Instead, you must be straightforward to show your intention and tell them the most basic information, plus the name of your referees.



\section{Recommendation}
The usage of the recommendation letter might be different, but the purpose is the same: evaluate the person objectively and properly, which helps the referee ``turn the ideal into reality''. It should be noted that the main part of the recommendation letter should speak with facts, or the credibility of the referrer is easy to discount. Additionally, since the recommendation letter is time-sensitive, once you decide to refuse, do not delay it for a long time to notify the other party; once you promise to write, must finish it on time.

Writing recommendation letters is part of the academic service, therefore, you should follow the professional ethics when writing recommendation letters, and avoid the sacred professional mission. Do not live up to the trust of students and their respect for personality.



\section{Review}
Since I do not have any relevant life experience about reviewing the manuscript. Section~7.3 seems incomprehensible to me, there may be some deviations between my summary and what the author wants to express. Therefore, I will summarize the last two chapters together.

Reviewing is a part of academic service, basically without remuneration, which is the researcher's voluntary labor and selfless dedication to the academic world.
It can be seen that this kind of academic service is essentially a win-win situation. On the one hand, academic journals rely on reviewers to ensure the publication of high-quality research papers. On the other hand, reviewers are exposed to the research results in the field earlier than others. which results in many positive effects on their own research. Of course, reviewing is not mandatory, when you are very busy at the moment, you can completely reject the invitation, optionally, the best approach is to help find some new reviewers.

There is a certain similarity between the review and the comment, but the time spent on reviewing the manuscript greatly exceeds the comment. The reviewer mainly allocates time to the careful examination of the certification process, while the commenter just summarizes the main content of the published paper, and attach their own subjective evaluation.
