% !Mode:: "TeX:UTF-8"
% 正文摘要内容
\setlength{\parskip}{1ex}
\begin{abstract}
The dragon will be a wonderful memory for your son or daughter, and our model will make dragon training a reality, if the dragon is real. 

We start with the growth of dragons, assuming that the indicators that can truly reflect the growth of dragons are related to functions, weight, diet, changes or other characteristics related to animals. This is a multivariate nonlinear objective programming model. After data transformation, the model is established for solution. With the growth of the dragon, the total amount of environmental resources is constantly changing, which means that the total growth will slow down, and the retarded growth model will follow.We got a lot of valuable data, such as the ecological demand of the dragon: 13.54 sheep/day, 808.26kg of vegetables/day. The population density of sheep was $0.548 /km^2$.

The ecological impact of dragons is a problem within the planning. We made assumptions about the energy demand based on the data of raptors. The region where the dragon lives can provide different levels of help to the dragon. Collect regional information, and use the method of dimensionality reduction to classify different regions. We have also expanded from one dragon to many, taking into account the impact of different climatic regions. The living space a dragon needs is 824$km^2/day$. Moreover, the interaction between dragons is studied innovatively, considering the competition between dragons and the attraction between dragons of the opposite sex.

The migration of the dragon is an important part of the survival of the species. Multivariate analysis is used to determine the ecological factors between different environments. The impact of the change can be determined by establishing a corresponding analysis between the migration of the dragon and the resources needed for its growth.

In addition, we analyze the performance of our model under various conditions, and modify our model to accommodate to them. We also mixed C++ and Python, using TDD architecture, greatly improve the program extensibility and readability. To sum up, our model is a feasible and reasonable model which can accommodate to various situations.
\end{abstract}